EUC_PVE

### 2014-09-03 markdowns/master.rmd
fixed soilN part of markdown script
change to C gain model and master.Rmd

```{r leaf area plot}
source("master_scripts/leafarea_plotting.R")
```

@@

```{r root:shoot plots }
source("master_scripts/rootshoot_plotting.R")
```

@@

```{r aci means plots }
source("master_scripts/aci_plotting.R")
```

@@

```{r water potential plots}
source("clean scripts/seedling water potential.R")
```

@@

```{r Cgain vs Cmass }
cgain<- read.csv("calculated data/euc_cgain.csv")
cgain$volume <- as.factor(cgain$volume)

@@

```{r Soil N percent}
source("master_scripts/soilN_plotting.R")
```

Predicted responses of Amax on a mass basis to leaf starch and N levels
```{r Amass vs TNC and N}
#source(("master_scripts/photochem_predict.R")
```

>>>>

```{r leafareaplot}
source("master_scripts/leafarea_plotting.R")
```

@@

```{r rootshootplots }
source("master_scripts/rootshoot_plotting.R")
```

asat and amax

```{r photosynthesisplotting}
source("master_scripts/A_plotting.R")
```

@@

```{r acimeansplots }
source("master_scripts/aci_plotting.R")
```

@@

```{r waterpotentialplots}
source("clean scripts/seedling water potential.R")
```

@@

```{r CgainvsCmass }
cgain<- read.csv("calculated data/euc_cgain.csv")
cgain$volume <- as.factor(cgain$volume)

@@

```{r SoilNpercent}
source("master_scripts/soilCN_plotting.R")
```

Predicted responses of Amax on a mass basis to leaf starch and N levels
```{r AmassvsTNCandN}
source("master_scripts/photochem_predict.R")
```
